### 2024-09-10 conteudo/introduction/intro.tex
fazendo as mudancas de acordo com as sugestoes

Representing 3.77\% of personal desktops and 70,69\% of smartphones worldwide, the Linux kernel is an open-source 
project providing value to billions of people daily. The magnitude that the project has reached over the years makes 
the addition of features, as well as handling bugs and security vulnerabilities, potentially affect a significant 
number of people, demonstrating the importance of maintaining the kernel.

>>>>

Representing 96,3\% of the top one million web servers and 85\% of smartphones worldwide, the Linux kernel is an open-source 
project providing value to billions of people daily. The magnitude that the project has reached over the years makes 
the addition of features, as well as handling bugs and security vulnerabilities, potentially affect a significant 
number of people, demonstrating the importance of maintaining the kernel \citep{linuxdata}.

### 2024-09-10 conteudo/resumoabstract.tex
fazendo as mudancas de acordo com as sugestoes

O kernel Linux é um projeto de código aberto amplamente utilizado, alimentando 3,77\% 
dos desktops pessoais e 70,69\% dos smartphones em todo o mundo. Dada a sua extensa 
base de usuários, qualquer adição de recursos, correção de bugs ou tratamento de 
vulnerabilidades de segurança pode impactar milhões de pessoas. Manter o kernel é 
uma tarefa enorme, envolvendo mais de 19 milhões de linhas de código e contribuições 
de mais de mil desenvolvedores. Devido à escala do projeto, nem todas as contribuições 
seguem as melhores práticas, resultando em artefatos de código de baixa qualidade que 
podem complicar a manutenção e o desenvolvimento de novos recursos. Um desses artefatos 
é a duplicação de código, que é o foco desta pesquisa. As ferramentas existentes 
para detectar duplicação de código normalmente comparam dois artefatos de código para 
determinar se são duplicatas. No entanto, essas ferramentas não são adequadas para 
identificar duplicações em bases de código em grande escala, como o kernel Linux, nem 
oferecem orientações sobre como resolver as duplicações detectadas. Apesar das 
pesquisas tanto na literatura formal quanto na cinza, as soluções existentes não 
conseguem resolver os desafios específicos do kernel Linux. Para abordar esse tema, 
esta pesquisa foca em dois objetivos principais. Primeiro, propõe uma nova ferramenta 
para identificar duplicações de código dentro do kernel Linux. Segundo, analisa as 
duplicações identificadas para extrair padrões e métodos de refatoração, oferecendo 
orientações para futuros contribuintes.

@@

The Linux kernel is a widely used open-source project, powering 3.77\% of personal desktops 
and 70.69\% of smartphones worldwide. Given its extensive user base, any addition of features, 
bug fixes, or handling of security vulnerabilities can impact millions. Maintaining the kernel 
is an enormous task, involving more than 19 million lines of code and contributions from over 
thirteen thousand developers. Due to the scale of the project, not all contributions adhere to best 
practices, resulting in poor-quality code artifacts that may complicate maintenance and feature 
development. One such artifact is code duplication, which is the focus of this research. 
Existing tools for detecting code duplication typically compare two code artifacts to determine 
if they are duplicates. However, these tools are not well-suited for identifying duplications 
in large-scale codebases like the Linux kernel, nor do they guide on resolving detected 
duplications. Despite searches in both formal and gray literature, existing solutions fall 
short of addressing the specific challenges of the Linux kernel. To address this topic, this 
research focuses on two key goals. First, it proposes a new tool to identify code duplications 
within the Linux kernel. Second, it analyzes the identified duplications to extract patterns 
and refactoring methods, offering guidance to future contributors.

>>>>

O kernel Linux é um projeto de software livre amplamente utilizado, alimentando 96,3\% 
dos um milhão maiores servidores web e 85\% dos smartphones em todo o mundo. Dada a sua extensa 
base de usuários, qualquer adição de recursos, correção de bugs ou tratamento de 
vulnerabilidades de segurança pode impactar milhões de pessoas. Manter o kernel é 
uma tarefa enorme, envolvendo mais de 19 milhões de linhas de código e contribuições 
de mais de mil desenvolvedores. Devido à escala do projeto, nem todas as contribuições 
seguem as melhores práticas, resultando em artefatos de código de baixa qualidade que 
podem complicar a manutenção e o desenvolvimento de novos recursos. Um desses artefatos 
é a duplicação de código, que é o foco desta pesquisa. As ferramentas existentes 
para detectar duplicação de código normalmente comparam dois artefatos de código para 
determinar se são duplicatas. No entanto, essas ferramentas não são adequadas para 
identificar duplicações em bases de código em grande escala, como o kernel Linux, nem 
oferecem orientações sobre como resolver as duplicações detectadas. Apesar das 
pesquisas tanto na literatura formal quanto na cinza, as soluções existentes não 
conseguem resolver os desafios específicos do kernel Linux. Para abordar esse tema, 
esta pesquisa foca em dois objetivos principais. Primeiro, propõe uma nova ferramenta 
para identificar duplicações de código dentro do kernel Linux. Segundo, analisa as 
duplicações identificadas para extrair padrões e métodos de refatoração, oferecendo 
orientações para futuros contribuidores.

@@

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project, powering
96.3\% of the top one million web servers 
and 85\% of smartphones worldwide. Given its extensive user base, any addition of features, 
bug fixes, or handling of security vulnerabilities can impact millions. Maintaining the kernel 
is an enormous task, involving more than 19 million lines of code and contributions from over 
thirteen thousand developers. Due to the scale of the project, not all contributions adhere to best 
practices, resulting in poor-quality code artifacts that may complicate maintenance and feature 
development. One such artifact is code duplication, which is the focus of this research. 
Existing tools for detecting code duplication typically compare two code artifacts to determine 
if they are duplicates. However, these tools are not well-suited for identifying duplications 
in large-scale codebases like the Linux kernel, nor do they guide on resolving detected 
duplications. Despite searches in both formal and gray literature, existing solutions fall 
short of addressing the specific challenges of the Linux kernel. To address this topic, this 
research focuses on two key goals. First, it proposes a new tool to identify code duplications 
within the Linux kernel. Second, it analyzes the identified duplications to extract patterns 
and refactoring methods, offering guidance to future contributors.
